\section*{Problem 1: 2D Navier--Stokes Solver for the Taylor--Green Vortex}

In this assignment, you will extend your pressure projection solver to a full incompressible Navier--Stokes solver in two dimensions. You will simulate the decay of the \emph{Taylor--Green vortex}, a canonical benchmark for transitional and decaying turbulence.

\subsection*{Governing Equations}

We consider the two-dimensional Navier--Stokes equations in the incompressible limit and non-dimensional form:
\begin{align}
  \frac{\partial u}{\partial x} + \frac{\partial v}{\partial y} &= 0, \label{eq:continuity} \\
  \frac{\partial u}{\partial t} + \frac{\partial uu}{\partial x} + \frac{\partial uv}{\partial y} &= -\frac{\partial p}{\partial x} + \frac{1}{\mathrm{Re}} \left( \frac{\partial^2 u}{\partial x^2} + \frac{\partial^2 u}{\partial y^2} \right), \label{eq:umom} \\
  \frac{\partial v}{\partial t} + \frac{\partial uv}{\partial x} + \frac{\partial vv}{\partial y} &= -\frac{\partial p}{\partial y} + \frac{1}{\mathrm{Re}} \left( \frac{\partial^2 v}{\partial x^2} + \frac{\partial^2 v}{\partial y^2} \right), \label{eq:vmom}
\end{align}
where $\mathrm{Re}$ is the Reynolds number.

\subsection*{Domain and Grid}

\begin{itemize}
  \item Domain: $[0, 2\pi]^2$
  \item Uniform (staggered) grid: $64 \times 64$
  \item Periodic boundary conditions in all directions
\end{itemize}

\subsection*{Initial Condition (Taylor--Green Vortex)}

\begin{align}
  u(x,y; t=0) &= \sin(x)\cos(y), \label{eq:ic_u} \\
  v(x,y; t=0) &= -\cos(x)\sin(y). \label{eq:ic_v}
\end{align}

\subsection*{Numerical Method}

Use a \emph{fractional step (projection) method} with second-order spatial discretization and Crank--Nicolson time integration for viscous terms. Use the Thomas algorithm for solving the viscous terms implicitly (tridiagonal solver in $x$- and $y$-directions using ADI splitting). Use the Sherman--Morrison correction for periodic boundary conditions. Use multigrid for the pressure Poisson equation.

\subsubsection*{Staggered Variable Arrangement}

For cell $(i,j)$, store velocity $u$ at the barycenter of the left face ($u_{i-\frac{1}{2},j}$), $v$ at the barycenter of the bottom face ($v_{i,j-\frac{1}{2}}$), and pressure $p$ at the cell center ($p_{i,j}$). The solenoidal constraint is discretized as:
\begin{equation}
  \nabla \cdot \mathbf{u}\big|_{i,j} \approx \frac{u_{i+\frac{1}{2},j} - u_{i-\frac{1}{2},j}}{\Delta x} + \frac{v_{i,j+\frac{1}{2}} - v_{i,j-\frac{1}{2}}}{\Delta y}. \label{eq:div}
\end{equation}

\subsubsection*{Spatial Discretization (u-momentum)}

Convective term in $x$:
\begin{equation}
  \left.\frac{\partial uu}{\partial x}\right|_{i-\frac{1}{2},j} \approx \frac{u_{i,j}^2 - u_{i-1,j}^2}{\Delta x} \label{eq:conv_x}
\end{equation}

Convective term in $y$:
\begin{equation}
  \left.\frac{\partial uv}{\partial y}\right|_{i-\frac{1}{2},j} \approx \frac{u_{i-\frac{1}{2},j+\frac{1}{2}} v_{i-\frac{1}{2},j+\frac{1}{2}} - u_{i-\frac{1}{2},j-\frac{1}{2}} v_{i-\frac{1}{2},j-\frac{1}{2}}}{\Delta y} \label{eq:conv_y}
\end{equation}

Viscous term in $x$:
\begin{equation}
  \left.\frac{\partial^2 u}{\partial x^2}\right|_{i-\frac{1}{2},j} \approx \frac{u_{i+\frac{1}{2},j} - 2u_{i-\frac{1}{2},j} + u_{i-\frac{3}{2},j}}{\Delta x^2} \label{eq:visc_x}
\end{equation}

Viscous term in $y$:
\begin{equation}
  \left.\frac{\partial^2 u}{\partial y^2}\right|_{i-\frac{1}{2},j} \approx \frac{u_{i-\frac{1}{2},j+1} - 2u_{i-\frac{1}{2},j} + u_{i-\frac{1}{2},j-1}}{\Delta y^2} \label{eq:visc_y}
\end{equation}

Pressure term in $x$:
\begin{equation}
  \left.\frac{\partial p}{\partial x}\right|_{i-\frac{1}{2},j} \approx \frac{p_{i,j} - p_{i-1,j}}{\Delta x} \label{eq:pres_x}
\end{equation}

Additional interpolations:
\begin{align}
  u_{i,j} &= \frac{1}{2}\left(u_{i-\frac{1}{2},j} + u_{i+\frac{1}{2},j}\right), \label{eq:u_interp} \\
  u_{i-\frac{1}{2},j-\frac{1}{2}} &= \frac{1}{2}\left(u_{i-\frac{1}{2},j} + u_{i-\frac{1}{2},j-1}\right), \label{eq:u_half_interp} \\
  v_{i-\frac{1}{2},j-\frac{1}{2}} &= \frac{1}{2}\left(v_{i,j-\frac{1}{2}} + v_{i-1,j-\frac{1}{2}}\right). \label{eq:v_half_interp}
\end{align}

\textbf{Observations:}
\begin{enumerate}
  \item All approximations are centered in space and formally second-order accurate.
  \item When coding, use $u(i,j) = u_{i-\frac{1}{2},j}$, $v(i,j) = v_{i,j-\frac{1}{2}}$, and $p(i,j) = p_{i,j}$.
  \item The $v$-momentum equation can be obtained readily from the proposed discretization of the $u$-momentum equation.
\end{enumerate}

\subsubsection*{Temporal Discretization -- Fractional Step Method}

Following Kim and Moin (1985), the method combines Adams--Bashforth for convective terms with Crank--Nicolson for viscous terms, and a projection step for pressure coupling.

\textbf{Step 1.} Advance momentum without pressure. Let $H$ denote the convective term:
\begin{equation}
  \frac{\mathbf{u}^\star_{i,j} - \mathbf{u}^n_{i,j}}{\Delta t} = \frac{3}{2}H^n_{i,j} - \frac{1}{2}H^{n-1}_{i,j} + \frac{1}{2\,\mathrm{Re}}\left(\frac{\delta^2}{\delta x^2} + \frac{\delta^2}{\delta y^2}\right)\left(\mathbf{u}^\star_{i,j} + \mathbf{u}^n_{i,j}\right). \label{eq:step1}
\end{equation}

Using approximate factorization (ADI splitting), this becomes two tridiagonal solves:
\begin{align}
  \left(1 - \frac{\Delta t}{2}\frac{1}{\mathrm{Re}}\frac{\delta^2}{\delta x^2}\right)\Delta \mathbf{u}^{\star\star}_{i,j} &= \frac{\Delta t}{2}\left(3H^n_{i,j} - H^{n-1}_{i,j}\right) + \frac{\Delta t}{\mathrm{Re}}\left(\frac{\delta^2}{\delta x^2} + \frac{\delta^2}{\delta y^2}\right)\mathbf{u}^n_{i,j}, \label{eq:adi_x} \\
  \left(1 - \frac{\Delta t}{2}\frac{1}{\mathrm{Re}}\frac{\delta^2}{\delta y^2}\right)\Delta \mathbf{u}^\star_{i,j} &= \Delta \mathbf{u}^{\star\star}_{i,j}, \label{eq:adi_y}
\end{align}
followed by the velocity update $\mathbf{u}^\star_{i,j} = \mathbf{u}^n_{i,j} + \Delta \mathbf{u}^\star_{i,j}$.

\textbf{Step 2.} Solve the pressure Poisson equation:
\begin{equation}
  \nabla \cdot \left(\nabla p^{n+1}\right)_{i,j} = \frac{1}{\Delta t}\nabla \cdot \mathbf{u}^\star\big|_{i,j}. \label{eq:ppe}
\end{equation}

\emph{Crucial observation:} The Laplacian in the pressure Poisson equation must be discretized exactly using the gradient and divergence operators from Steps 2 and 3.

\textbf{Step 3.} Correct the velocity:
\begin{equation}
  \mathbf{u}^{n+1}_{i,j} = \mathbf{u}^\star_{i,j} - \Delta t\,\nabla p^{n+1}\big|_{i,j}. \label{eq:correction}
\end{equation}

\subsubsection*{Time Stepping}

Choose $\Delta t$ such that:
\[
  \mathrm{CFL} = \frac{u_{\max}\Delta t}{\Delta x} \lesssim 0.5
\]
Simulate until $t = 10$.

\subsection*{Questions}

\subsubsection*{(a) Numerical Method Description}

% TODO: Provide a brief description of your numerical method, including:
% - Discretization of convective and diffusive terms
% - Structure of the Helmholtz solver
% - Linear solvers used

\textbf{Solution:}


\subsubsection*{(b) Incompressibility Verification}

% TODO: Plot either the max or L2 norm of divergence vs time

\textbf{Solution:}


\subsubsection*{(c) Kinetic Energy}

% TODO: Compute and plot kinetic energy E(t) = 1/2 int |u|^2 dV
% Compare with expected decay behavior (analytic solution from HW1)

\textbf{Solution:}


\subsubsection*{(d) Flow Visualization}

% TODO: Contours or slices of velocity magnitude and pressure

\textbf{Solution:}


\subsubsection*{(e) Report}

% TODO: Report the following:
% - Time step size
% - Solver tolerances and number of iterations
% - Computational cost
% - Compare velocity field to analytical solution for 2D Taylor-Green vortex (see HW 1)

\textbf{Solution:}


\subsubsection*{(f) Code}

See attached source code in the appendix.
