% This file documents AI-assisted interactions for ME 523 HW7.
% Include in a parent .tex file with: \input{prompts}
%!TEX root = hw_7.tex

\section*{AI Use Documentation}

\subsection*{Interaction 1}

\textbf{Prompt:}
\begin{quote}
Set up the C++ project structure for a 2D incompressible Navier-Stokes solver using Kokkos and Trilinos. Use the Chorin projection method on a staggered MAC grid. Organize as a hybrid library with header-only templated code and compiled source files for non-templated components (pressure solver, CSV output, physics kernels). Include Spack-based dependency management, CMake build system, and Doxygen documentation.
\end{quote}

\textbf{Response summary:}
Claude scaffolded the full project: \texttt{include/} headers for the solver pipeline (grid, boundary conditions, initial conditions, integrators, physics, pressure solver, output, and a templated \texttt{Solver<BC, Integrator>}), compiled \texttt{src/} sources for \texttt{PressureSolver}, \texttt{CSVOutput}, and \texttt{physics::} functions, Spack environment definitions for multiple machines, CMake build files, GitHub Actions CI for Doxygen deployment, and the main driver in \texttt{apps/ns\_solver.cpp}. Function stubs with TODOs were left for the actual numerical implementations.

\textbf{Date and Model:} Claude Opus 4.6, 2026-04-12

\subsection*{Interaction 2}

\textbf{Prompt:}
\begin{quote}
Look at the solver files, the physics files etc to check what is causing the error:
\texttt{Kokkos::View ERROR: attempt to access inaccessible memory space (label="ke\_history")}.
\end{quote}

\textbf{Response summary:}
Claude identified that the \texttt{ke\_history} and \texttt{div\_history} views in \texttt{SimState} were declared as \texttt{Kokkos::View<double*>} with no explicit memory space. Because Kokkos is built with CUDA as the default execution space on this machine (\texttt{ncam} spack environment: \texttt{kokkos +cuda cuda\_arch=120}), the default memory space is \texttt{CudaSpace}. Host code in \texttt{solver.hpp} was then trying to directly index these device views after \texttt{parallel\_reduce} returned a host scalar, which Kokkos correctly rejected. The fix was to declare both views as \texttt{Kokkos::View<double*, Kokkos::HostSpace>} and remove the now-redundant \texttt{create\_mirror\_view\_and\_copy} calls in \texttt{output.cpp}.

\textbf{Date and Model:} Claude Sonnet 4.6, 2026-04-13

\subsection*{Interaction 3}

\textbf{Prompt:}
\begin{quote}
Why do the last tests for KE and divergence both fail? Is there something wrong with how it is implemented? Is it an issue with the test or the source code?
\end{quote}

\textbf{Response summary:}
Claude identified two separate bugs introduced by the partner's PR on the \texttt{diagnostics} branch.
(1) \textbf{KE test stale}: Commit \texttt{f77dcf9} correctly added area-weighting (\texttt{* dx * dy}) to \texttt{compute\_kinetic\_energy} to compute the domain-integrated kinetic energy, but the \texttt{test\_uniform\_field} expected value (130.0) was never updated. Claude updated the expected value to \texttt{130.0 * grid.dx * grid.dy} with an explanatory comment.
(2) \textbf{Divergence normalization wrong}: \texttt{compute\_l2\_divergence} divided \texttt{sum\_div\^{}2} by \texttt{nx*ny} before taking the square root, yielding an RMS rather than an L2 norm. \texttt{test\_known\_divergence} expected the true L2 norm \texttt{sqrt(sum div\^{}2)}. Claude removed the division. Both fixes were committed to a new branch \texttt{div-ke-correction} and submitted as PR \#73.

\textbf{Date and Model:} Claude Sonnet 4.6, 2026-04-13

\subsection*{Interaction 4}

\textbf{Prompt:}
\begin{quote}
Look at the current setup in test and physics for computing divergence. I want this \texttt{l2\_div} to mean RMS for mesh refinement purposes. Recall the branch we made \texttt{div-ke-correction}, fix it to be consistent with this version we had switched it to a true L2 norm. Then build and run all tests and the solver app to ensure it works.
\end{quote}

\textbf{Response summary:}
Claude compared the \texttt{diagnostics} branch (RMS: \texttt{sqrt(sum\_div\^{}2 / (nx*ny))}, expected 2.0) against \texttt{div-ke-correction} (true L2: \texttt{sqrt(sum\_div\^{}2)}, expected \texttt{2*sqrt(nx*ny)}). On \texttt{div-ke-correction}, the implementation used the true L2 but the test expected value had already been partially updated to the RMS value with leftover contradictory comments. Claude fixed \texttt{src/physics.cpp} to divide by \texttt{nx*ny} before the square root and cleaned up the comment in \texttt{tests/test\_l2\_divergence.cpp}. Build succeeded and all 3 tests (OutputTest, KineticEnergyTest, L2DivergenceTest) passed. The PR \#73 description was updated to clarify that \texttt{compute\_l2\_divergence} returns an RMS (grid-size-independent metric suitable for mesh refinement studies), not a true L2 norm.

\textbf{Date and Model:} Claude Sonnet 4.6, 2026-04-13

\subsection*{Interaction 5}

\textbf{Prompt:}
\begin{quote}
Grab the multigrid pressure solver branch and try to build and run tests and app to make sure it works. Then merge in new main stuff and make a new pull request.
\end{quote}

\textbf{Response summary:}
Build failed with 10 NVCC errors: ``The enclosing parent function for an extended \texttt{\_\_host\_\_ \_\_device\_\_} lambda cannot have private or protected access within its class.'' All \texttt{KOKKOS\_LAMBDA}-containing helper methods of \texttt{PressureSolver} were in the \texttt{private:} section; NVCC cannot generate helper types for extended device lambdas in that scope. Fix: moved \texttt{Level} struct and all helper methods to \texttt{public:} in \texttt{pressure\_solver.hpp}, keeping only data members private. After pulling the remote branch (which had merged main/div-ke-correction), a second error appeared: \texttt{test\_pressure\_solver.cpp} used the old single-argument \texttt{SimState(grid)} constructor, changed to require \texttt{n\_steps} as a second argument by the div-ke-correction merge. Both call sites updated to \texttt{SimState(grid, 1)}. Build succeeded, all 4 tests passed (OutputTest, PressureSolverTest, KineticEnergyTest, L2DivergenceTest), and \texttt{ns\_solver} ran cleanly. Fixes committed to new branch \texttt{multigrid-cuda-compat} and submitted as PR \#75.

\textbf{Date and Model:} Claude Sonnet 4.6, 2026-04-13

\subsection*{Interaction 7}

\textbf{Prompt:}
\begin{quote}
Pick issue \#88 (flow visualization). Copy and rename existing plots from the data directory. Show all Re and CFL like the other two figures.
\end{quote}

\textbf{Response summary:}
Claude copied all 12 flow-visualization images from the run directories (\texttt{data/run\_64\_64\_\{Re\}\_cfl\{CFL\}/figures/}) into \texttt{hw\_7\_tex/images/} with descriptive names (\texttt{velocity\_magnitude\_re\{Re\}\_cfl\{CFL\}.png} and \texttt{pressure\_re\{Re\}\_cfl\{CFL\}.png} for Re $\in \{10, 100, 1000\}$ and CFL $\in \{0.2, 0.5\}$). Two figure environments were added to the \texttt{(d) Flow Visualization} subsection of \texttt{prob1.tex}, each with two subfigure rows (CFL = 0.2 and CFL = 0.5) of three \texttt{0.32\textbackslash textwidth} images (Re = 10, 100, 1000), matching the layout of the divergence and kinetic energy figures in parts (b) and (c). Issue \#88 was closed.

\textbf{Date and Model:} Claude Haiku 4.5, 2026-04-13

\subsection*{Interaction 6}

\textbf{Prompt:}
\begin{quote}
I was told that the Thomas algorithm is bad for GPU use since it requires serial tridiagonal sweeps. How would we modify the solver to still do Crank-Nicolson but use a GPU-friendly implicit viscous solve instead? Design and implement this on a new branch \texttt{time-integration}.
\end{quote}

\textbf{Response summary:}
Claude designed a Crank-Nicolson integrator that replaces the serial Thomas algorithm with a Red-Black Gauss-Seidel (RBGS) iteration for the implicit viscous solve. The operator being inverted is $(I - \frac{\Delta t}{2 Re}\nabla^2)\mathbf{u}^* = \mathbf{b}$, which is SPD, so RBGS converges. Each RBGS pass is two fully parallel \texttt{Kokkos::MDRangePolicy} kernels (red cells then black cells), making it GPU-friendly. The update formula uses \texttt{physics::laplacian} for consistency with the rest of the codebase.

The following changes were made across the codebase:

\textbf{Split RHS functions} (\texttt{src/physics.cpp}, \texttt{include/physics.hpp}):
Added \texttt{compute\_u\_conv\_rhs}, \texttt{compute\_u\_diff\_rhs}, \texttt{compute\_v\_conv\_rhs}, \texttt{compute\_v\_diff\_rhs} to separate convective and diffusive contributions, which Crank-Nicolson treats differently (explicit convection, semi-implicit diffusion). The original \texttt{compute\_u\_rhs} / \texttt{compute\_v\_rhs} were kept for \texttt{ForwardEuler}.

\textbf{ViscousSolver} (\texttt{include/viscous\_solver.hpp}, header-only):
New struct with \texttt{solve\_u} and \texttt{solve\_v} methods. Each iterates up to \texttt{max\_iters=50} RBGS sweeps, calling \texttt{bc.apply\_u}/\texttt{bc.apply\_v} between iterations to keep ghost cells consistent. Templated on \texttt{BC} to thread the boundary condition through the solve loop. Convergence is checked via RMS residual of $(I - \alpha\nabla^2)u^* - \text{rhs}$.

\textbf{Boundary conditions refactored} (\texttt{include/boundary\_conditions.hpp}):
Both \texttt{LidDrivenCavityBC} and \texttt{PeriodicBC} had their monolithic \texttt{apply(SimState\&)} split into separate \texttt{apply\_u(MacGrid2D\&, View)} and \texttt{apply\_v(MacGrid2D\&, View)} methods so the viscous solver can enforce BCs on scratch views during RBGS iterations without access to the full \texttt{SimState}.

\textbf{Integrators refactored} (\texttt{include/integrator.hpp}):
\texttt{ForwardEuler::predict} updated to accept a \texttt{BC} template parameter (unused, kept for interface uniformity). New \texttt{CrankThatNicolson} integrator added: assembles the explicit CN RHS ($\mathbf{u} + \Delta t\,C(\mathbf{u}) + \frac{\Delta t}{2}D(\mathbf{u})$), sets the initial guess for $\mathbf{u}^*$, then calls \texttt{ViscousSolver::solve\_u}/\texttt{solve\_v}. All member \texttt{Kokkos::View} captures in \texttt{KOKKOS\_LAMBDA} use explicit local copies with declared type \texttt{Kokkos::View<double**>} to avoid implicit \texttt{this}-pointer capture (which is invalid on device).

\textbf{Solver wired up} (\texttt{include/solver.hpp}, \texttt{apps/ns\_solver.cpp}):
\texttt{Solver} template instantiated as \texttt{Solver<PeriodicBC, CrankThatNicolson>} for the Taylor-Green vortex run.

\textbf{Tests} (\texttt{tests/test\_viscous\_solver.cpp}, \texttt{tests/test\_integrators.cpp}):
Six new tests added: zero RHS converges to zero; constant RHS with periodic BC converges to that constant (since $\nabla^2 C = 0$); \texttt{ForwardEuler} leaves a uniform field unchanged; \texttt{CrankThatNicolson} leaves a uniform field unchanged; \texttt{CrankThatNicolson} dissipates kinetic energy from a sinusoidal field at low Re. All 6 tests pass alongside the existing 4.

\textbf{Date and Model:} Claude Sonnet 4.6, 2026-04-13
